---
title: "Cars dataset"
author: "Sergio Giraldo"
date: "July, 2019"
output: html_document
---

## Analysis

The data used for the analysis is the `mtcars` data set, a dataset builtin in R. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973 and 1974 models).

### Loading the data

```{r}
data(mtcars)
mtcars
mtcarsOriginal <- mtcars
```

### Exploring the data

Let's explore data size

```{r}
dim(mtcars)
```

Structure of the data:

```{r}
str(mtcars)
```

This is the purpose for each feature:

* **mpg:** Miles/(US) gallon
*	**cyl:**	Number of cylinders
*	**disp:**	Displacement (cu.in.)
*	**hp:**	Gross horsepower
*	**drat:**	Rear axle ratio
*	**wt:**	Weight (1000 lbs)
*	**qsec:**	1/4 mile time
*	**vs:**	V/S
*	**am:**	Transmission (0 = automatic, 1 = manual)
*	**gear:**	Number of forward gears
*	**carb:**	Number of carburetors

Of particular interest is `mpg` (Miles/US gallon) variable as result variable.

### Data transformation

For interpretability, let's transform some of the variables

```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

Also, let's convert predictor variable `am` to factor levels `Automatic` and `Manual`.

```{r}
mtcars$am <- factor(mtcars$am, labels = c("Automatic", "Manual"))
```

Figure below shows how miles per US Gallon (`mpg`) relates to transmission type and gives a hint manual transmission is better. 

```{r, results='hide', warning=FALSE, message=FALSE}
library(ggplot2)
```

```{r}
ggplot(mtcars, aes(x=am, y=mpg, fill=am)) +
  geom_boxplot() +
  ylab("Miles per US gallon") +
  xlab("Transmission") +
  guides(fill=FALSE)
```

This can be confirmed comparing averages of Miles per Gallon by transmission type

```{r}
aggregate(mpg ~ am, data = mtcars, mean)
```

Notice the difference between them. It seems manual transmissions gets better gas mileage and needs to investigate if this impact is due only to transmission type or a mix of other car characteristics.

### Model selection

Let's compare a simple linear model based only on `mpg` and `am` variables. Then let's use an automatic model selection based on the R `step` function.

Let's start by looking at the variables correlation to the outcome `mpg`.

#### Correlation

To determine which predictor variables should be included in the regression model, let's build a correlation matrix and check how each of the variable is related to the `mpg` variable.

```{r}
# using the original mtcars without transformations
sort(cor(mtcarsOriginal)[1,])
```

The result shows that the most correlated variables to `mpg` (except `am` that needs to be included in the model) are `wt`, `cyl`, `disp` and `hp`. However it seems that `cyl` and `disp` are collinear and only `cyl` will be included in the model. 

The model will use as predictors the following variables: 

- `am`; 

- `wt`;

- `cyl`;

- `hp`. 

Except for the `am` variable, all the others have negative impact on the `mpg`, which is quite logical because the more important the car weight is, or the horse power, the fewer miles per gallon it can make. This will be confirmed later in the automatic model selection.

#### Linear regression models

Let's start the model testing with a simple model and single predictor variable `am`.

```{r}
fit1 <- lm(mpg ~ am, data = mtcars)
summary(fit1)
```

Interpreting the result, notice cars with manual transmission have **7.245** Miles per Gallon more than the automatic. However, R-squared value is **0.3598**, which means that only **35.98%** of the variance is explained by the model.

Let's understand the impact of the other variables in the result feature.

Let's try with automatic model selection

```{r}
fit2 <- step(lm(mpg ~ ., data = mtcars), trace=0, steps=1000, direction="both")
summary(fit2)
```

Notice the automatic model selection is based on the same variables that were chosen based on the correlation check, i.e., `am`, `wt`, `cyl` and `hp`.

This shows that the most negative influence on the Miles per gallon are cylinders (`cyl`) and weight (`wt`). For example, each increase in weight by 1000 lb (`wt`) decreases the `mpg` by **2.49683** miles. It is also quite expected that as more cylinders a car have, the more gas it will use. The same goes for horse power (`hp`). 

As for R-squared, value is **0.8659** which means that **86.59%** of the variation is explained by the model which indicates it's a robust and highly predictive model.

Comparing the model `fit1` to `fit2` using ANOVA, it shows the second model `fit2`, based on multi-variable regression, is superior to the first model.

```{r}
anova(fit1, fit2)
```

The p-value of **1.688e-08** endorses that conclusion.

### Diagnostics

Once the model is selected (`fit2`), the next thing to do would be to run some diagnostics and to look at the **Residuals** plot (refer to **Figure 1** in appendix). 

The normal Q-Q plot shows residual points located mostly near the line implying the residuals are normally distributed. The Residuals vs. Fitted plot show randomly scattered points above and below the 0 line. We cannot see any pattern which means it show normality and no evidence of heteroscedasticity.


## Conclusion

This analysis allowed to answer which type of transmission has a better MPG (Miles per gallon) average. The cars with manual transmissions tend to have a better gas millage on average. The best model `fit2` explained **86%** of the variance but there is still some amount of uncertainty. 

The most important influence seems to be the weight of the car as this can be seen in **Figure 2** in appendix. Maybe cars with automatic transmission tend to be heavier. It was also possible to quantify the MPG difference between automatic and manual transmissions.

## Appendix

### Figure 1: Diagnostic plots 

The normal Q-Q plot shows residual points located mostly near the line implying the residuals are normally distributed. The Residuals vs. Fitted plot show randomly scattered points above and below the 0 line. We cannot see any pattern which means it show normality and no evidence of heteroscedasticity.

```{r, results='hide', warning=FALSE, message=FALSE}
library(ggfortify)
```

```{r}
autoplot(fit2, data = mtcars, 
         colour = 'am', label.size = 3)
```

### Figure 2: Weight per transmission type

```{r, warning=F}
ggplot(mtcars, aes(x=am, y=wt, fill=am)) +
  geom_boxplot() +
  ylab("Weight") +
  xlab("Transmission") +
  ggtitle("Figure 2: Weight by transmission type") +
  guides(fill=FALSE)
```