---
title: "Predict gender using weight and height"
author: "Sérgio Giraldo"
date: "2019-07-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, include=FALSE}
library(readr)
library(caret)
library(dplyr)
library(ggplot2)
```


```{r}
#get the dataset
heights_weights <- read_csv("heights_weights.csv")

```

There are 5000 observations for men and 5000 for women, the dataset is balanced

```{r}
summary(heights_weights)

ggplot(heights_weights,aes(Height,Weight)) +
  geom_point(aes(colour = Male), 
             show.legend = F, size = 1)
```


Looking at the graph above, using just height and weight may not lead to good results. This could be improved by including more features.

For now, let's try a simple model using logistic regression. Notice the dataset is separated 80% for training and 20% for prediction.

```{r}
train <- heights_weights[1:8000,]
test <- heights_weights[8001:10000,]
```

## The model


## Training

```{r}
train$Male <- as.factor(as.numeric(as.character(train$Male)))

model <- glm(Male ~.,
              family=binomial,
              data=train)

print(summary(model))

plot(model)
```


### Predicting

```{r}
featureImportance <- varImp(model, scale = FALSE)
featureImportanceDf <- data.frame(FEATURE = row.names(featureImportance),
                                  IMPORTANCE = featureImportance$Overall)

featureImportanceDf %>% 
  mutate(IMPORTANCE = round(IMPORTANCE, 4)) %>% 
  arrange(-IMPORTANCE)

trainingPred <- predict(model,
                        train,
                        type = "response")

trainingPred <- data.frame(trainingPred) %>% 
  mutate(gender = as.factor(ifelse(trainingPred > 0.3, 1, 0)))

confusionMatrixCalculated <- confusionMatrix(data = trainingPred$gender,
                                             reference = train$Male)

print(confusionMatrixCalculated)
```

## Conclusions

Model reached a satisfactory accuracy of **91%**. 
This could be improved by enriching the dataset with others features.




