---
title: "Poll"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(DT)
library(forcats)
library(stringr)
library(ggplot2)
library(scales)
```

```{r load,results='hide', warning=FALSE, message=FALSE}
poll <- read_delim("poll.csv", ";", escape_double = FALSE, trim_ws = TRUE)
```

This is a poll about financial products.

It had `r nrow(poll)` answers between `r min(poll$"Date Submitted")` and `r max(poll$"Date Submitted")`.

```{r cleansing, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
poll$credit_card_limit <- gsub("(c|C)inco", "5", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(d|D)ois", "2", poll$credit_card_limit)
poll$credit_card_limit <- gsub("Trens", "3", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(s|S)ete", "7", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(o|O)ito", "8", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(q|Q)uinze", "15", poll$credit_card_limit)
poll$credit_card_limit <- gsub("000 (mil|MIL|Mil)", "000", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(\\d+)\\s{0,1}(mil|MIL|Mil)", "\\1000", poll$credit_card_limit)
poll$credit_card_limit <- gsub("mil", "1000", poll$credit_card_limit)
poll$credit_card_limit <- gsub(",00$", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\.00$", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\.", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\,", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\$", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("#", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\s?reais", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("(\\d+)\\s?k", "\\1000", poll$credit_card_limit)
poll$credit_card_limit <- gsub(",00", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("\\D", "", poll$credit_card_limit)
poll$credit_card_limit <- gsub("^0+$", NA, poll$credit_card_limit)
poll$credit_card_limit <- gsub("^$", NA, poll$credit_card_limit)

poll$account_limit <- gsub("(c|C)inco", "5", poll$account_limit)
poll$account_limit <- gsub("(d|D)ois", "2", poll$account_limit)
poll$account_limit <- gsub("Trens", "3", poll$account_limit)
poll$account_limit <- gsub("(s|S)ete", "7", poll$account_limit)
poll$account_limit <- gsub("(o|O)ito", "8", poll$account_limit)
poll$account_limit <- gsub("(q|Q)uinze", "15", poll$account_limit)
poll$account_limit <- gsub("000 (mil|MIL|Mil)", "000", poll$account_limit)
poll$account_limit <- gsub("(\\d+)\\s{0,1}(mil|MIL|Mil)", "\\1000", poll$account_limit)
poll$account_limit <- gsub("mil", "1000", poll$account_limit)
poll$account_limit <- gsub(",00$", "", poll$account_limit)
poll$account_limit <- gsub("\\.00$", "", poll$account_limit)
poll$account_limit <- gsub("\\.", "", poll$account_limit)
poll$account_limit <- gsub("\\,", "", poll$account_limit)
poll$account_limit <- gsub("\\$", "", poll$account_limit)
poll$account_limit <- gsub("#", "", poll$account_limit)
poll$account_limit <- gsub("\\s?reais", "", poll$account_limit)
poll$account_limit <- gsub("(\\d+)\\s?k", "\\1000", poll$account_limit)
poll$account_limit <- gsub(",00", "", poll$account_limit)
poll$account_limit <- gsub("\\D", "", poll$account_limit)
poll$account_limit <- gsub("^0+$", NA, poll$account_limit)
poll$account_limit <- gsub("^$", NA, poll$account_limit)

poll$proposed_credit_card_limit <- gsub("(c|C)inco", "5", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(d|D)ois", "2", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("Trens", "3", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(s|S)ete", "7", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(o|O)ito", "8", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(q|Q)uinze", "15", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("000 (mil|MIL|Mil)", "000", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(\\d+)\\s{0,1}(mil|MIL|Mil)", "\\1000", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("mil", "1000", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub(",00$", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\.00$", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\.", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\,", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\$", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("#", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\s?reais", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("(\\d+)\\s?k", "\\1000", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub(",00", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("\\D", "", poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("^0+$", NA, poll$proposed_credit_card_limit)
poll$proposed_credit_card_limit <- gsub("^$", NA, poll$proposed_credit_card_limit)

poll$proposed_account_limit <- gsub("(c|C)inco", "5", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(d|D)ois", "2", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("Trens", "3", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(s|S)ete", "7", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(o|O)ito", "8", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(q|Q)uinze", "15", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("000 (mil|MIL|Mil)", "000", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(\\d+)\\s{0,1}(mil|MIL|Mil)", "\\1000", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("mil", "1000", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub(",00$", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\.00$", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\.", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\,", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\$", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("#", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\s?reais", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("(\\d+)\\s?k", "\\1000", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub(",00", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("\\D", "", poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("^0+$", NA, poll$proposed_account_limit)
poll$proposed_account_limit <- gsub("^$", NA, poll$proposed_account_limit)

```

##Device 

```{r}

ggplot(poll) +
 aes(x = Device) +
 geom_bar(position = "dodge", fill = "#006d2c") +
  geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))

ggplot(poll, aes(x = as.factor(Device))) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#006d2c") +
  geom_text(aes(y = ((..count..)/sum(..count..)), 
              label = scales::percent((..count..)/sum(..count..))), 
              stat = "count", vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(y = "Percent", x = "Device")
```

##Browser

```{r}

poll %>% 
  mutate(browser_ = str_extract(Browser, "^([\\w\\-]+)"),
         browser_ = fct_collapse(browser_, 
                      Chrome = c("Chrome", "Chromium", "Samsung"), 
                      IE = c("Edge", "IE"))) %>%
  group_by(browser_) %>%
  mutate(N_aux = n()) %>%
  ungroup() %>%
  mutate(browser_ = fct_reorder(browser_, N_aux, .desc = TRUE)) %>%
  ggplot() +
   aes(x = browser_) +
   geom_bar(position = "dodge", fill = "#006d2c") +
    geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))

```

##OS
```{r}

poll %>% 
  mutate(os_ = str_extract(OS, "^([\\w\\-]+)"),
         os__ = fct_collapse(os_, 
                      Unix = c("Chrome", "Linux", "Ubuntu"))) %>%
  group_by(os_) %>%
  mutate(N_aux = n()) %>%
  ungroup() %>%
  mutate(os_ = fct_reorder(os_, N_aux, .desc = TRUE)) %>%
  ggplot() +
   aes(x = os_) +
   geom_bar(position = "dodge", fill = "#006d2c") +
    geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))
```

## Products used

```{r}
poll %>%
  group_by(products) %>%
  mutate(N_aux = n()) %>%
  ungroup() %>%
  mutate(products = fct_reorder(products, N_aux, .desc = TRUE)) %>%
  ggplot() +
   aes(x = products) +
   geom_bar(position = "dodge", fill = "#006d2c") +
   geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))
```


#Credit Card Limit
```{r}
  poll %>%
  filter(!is.na(credit_card_limit)) %>%
  mutate(credit_card_limit = as.numeric(credit_card_limit)) %>%
  group_by(credit_card_limit) %>%
  summarise(count=n()) %>%
  arrange()%>%
  datatable()

poll %>%
  filter(!is.na(credit_card_limit)) %>%
  mutate(credit_card_limit = as.numeric(credit_card_limit)) %>%
  mutate(credit_card_limit_categories = cut(credit_card_limit, 
                                         c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                         dig.lab = 6)) %>%
  ggplot() +
   aes(x = credit_card_limit_categories) +
   geom_bar(position = "dodge", fill = "#006d2c") +
   geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))


```

#Proposed Credit Card Limit
```{r}
  poll %>%
  filter(!is.na(proposed_credit_card_limit)) %>%
  mutate(proposed_credit_card_limit = as.numeric(proposed_credit_card_limit)) %>%
  group_by(proposed_credit_card_limit) %>%
  summarise(count=n()) %>%
  arrange() %>%
  datatable()

  poll %>%
  filter(!is.na(proposed_credit_card_limit)) %>%
  mutate(proposed_credit_card_limit = as.numeric(proposed_credit_card_limit)) %>%
  mutate(proposed_account_limit_categories = cut(proposed_credit_card_limit, 
                                         c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                         dig.lab = 6)) %>%
  ggplot() +
   aes(x = proposed_account_limit_categories) +
   geom_bar(position = "dodge", fill = "#006d2c") +
   geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))

```

#Account Limit
```{r}
  poll %>%
  filter(!is.na(account_limit)) %>%
  mutate(account_limit = as.numeric(account_limit)) %>%
  group_by(account_limit) %>%
  summarise(count=n()) %>%
  arrange() %>%
  datatable()
    
  poll %>%
  filter(!is.na(account_limit)) %>%
  mutate(account_limit = as.numeric(account_limit)) %>%
  mutate(account_limit_categories = cut(account_limit, 
                                         c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                         dig.lab = 6)) %>%
  ggplot() +
   aes(x = account_limit_categories) +
   geom_bar(position = "dodge", fill = "#006d2c") +
   geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))

```

#Proposed Account Limit
```{r}
  poll %>%
  filter(!is.na(proposed_account_limit)) %>%
  mutate(proposed_account_limit = as.numeric(proposed_account_limit)) %>%
  group_by(proposed_account_limit) %>%
  summarise(count=n()) %>%
  arrange() %>%
  datatable()

  poll %>%
  filter(!is.na(proposed_account_limit)) %>%
  mutate(proposed_account_limit = as.numeric(proposed_account_limit)) %>%
  mutate(proposed_credit_card_limit_categories = cut(proposed_account_limit, 
                                         c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                         dig.lab = 6)) %>%
  ggplot() +
   aes(x = proposed_credit_card_limit_categories) +
   geom_bar(position = "dodge", fill = "#006d2c") +
   geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))
```

#Is your account limit enough?
```{r}
  poll %>%
    filter(!is.na(account_limit_is_enough)) %>%
    ggplot() +
     aes(x = account_limit_is_enough) +
     geom_bar(position = "dodge", fill = "#006d2c") +
     geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))
```

Among who answered **Yes**, what is the limit distributuion?
*removed answers whose limit was greater than 100.000*

```{r}
  poll %>%
    filter(!is.na(account_limit_is_enough)) %>%
    filter(account_limit_is_enough == "Yes") %>%
    mutate(vl = as.numeric(account_limit)) %>%
    filter(vl < 100000) %>%
    select(vl) %>%
    summary()

poll %>%
  filter(!is.na(account_limit)) %>%
  mutate(account_limit = as.numeric(account_limit)) %>%
  mutate(account_limit_categories = cut(account_limit, 
                                            c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                            dig.lab = 6)) %>%
  ggplot(aes(x = account_limit_categories)) +
  geom_bar(aes(fill = account_limit_is_enough)) +
  labs(x = "Account Limit Intervals") +
  theme(axis.text.x = element_text(angle = 20))

```

#Is your Credit Card limit enough?
```{r}
  poll %>%
    filter(!is.na(credit_card_limit_is_enough)) %>%
    ggplot() +
     aes(x = credit_card_limit_is_enough) +
     geom_bar(position = "dodge", fill = "#006d2c") +
     geom_text(stat='count', aes(label=..count..), size = 3, position = position_stack(vjust = 0.5))
```

Among who answered **Yes**, what is the limit distributuion?
*removed answers whose limit was greater than 100.000*

```{r}
poll %>%
  filter(!is.na(credit_card_limit_is_enough)) %>%
  filter(credit_card_limit_is_enough == "Yes") %>%
  mutate(vl = as.numeric(credit_card_limit)) %>%
  filter(vl < 100000) %>%
  select(vl) %>%
  summary()

pollAux <-
  poll %>%
  filter(!is.na(credit_card_limit)) %>%
  filter(!is.na(credit_card_limit_is_enough)) %>%
  mutate(credit_card_limit = as.numeric(credit_card_limit)) %>%
  mutate(credit_card_limit_categories = cut(credit_card_limit, 
                                            c(-Inf, 1000, 3000, 5000, 10000, 20000, 30000, Inf),
                                            dig.lab = 6)) 
pollAux %>%
  ggplot(aes(x = credit_card_limit_categories)) +
  geom_bar(aes(fill = credit_card_limit_is_enough)) +
  labs(x = "Credit Card Limit Intervals") +
  theme(axis.text.x = element_text(angle = 20))

ggplot(pollAux, aes(x = as.factor(credit_card_limit_categories))) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#006d2c") +
  geom_text(aes(y = ((..count..)/sum(..count..)), 
              label = scales::percent((..count..)/sum(..count..))), 
              stat = "count", vjust = -0.25) +
  scale_y_continuous(labels = percent) +
  labs(y = "Percent", x = "Credit Card Limit") +
  facet_grid(~credit_card_limit_is_enough)  +
    theme(axis.text.x = element_text(angle = 20))

```
