---
title: "Product relationship"
author: "Sergio Giraldo"
date: "2019-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(readr)
library(arules)
library(arulesViz)
library(dplyr)
library(data.table)
library(magrittr)
library(UpSetR)
```

## Motivation

Given a base of user with a large set of product offerinngs, let's study which products are used together.


## Analysis

There are 5.497.517 distinct customers.

```{r load, include=FALSE}
results <- read.csv2("results.csv")
colnames(results) <- c("CUSTOMER_ID","PRODUCT")
```

```{r one-hot-encoding, include=FALSE}
#results with one hot encoding, not grouped
resultsOneHotEncoding <- results
for(unique_value in unique(resultsOneHotEncoding$PRODUCT)){
  resultsOneHotEncoding[unique_value] <- ifelse(resultsOneHotEncoding$PRODUCT == unique_value, 1, 0)
}
resultsOneHotEncoding$PRODUCT <- NULL

#results with one hot encoding, grouped
resultsOneHotEncodingGrouped <- resultsOneHotEncoding %>% group_by(CUSTOMER_ID) %>% summarise_all(sum)
```

```{r binarized}
#results with binary representation
resultsGrouped <- resultsOneHotEncoding

resultsGrouped$PRODUCTS <-
paste0(
resultsGrouped$PRODUCT_P1,
resultsGrouped$PRODUCT_P2,
resultsGrouped$PRODUCT_P3,
resultsGrouped$PRODUCT_P4,
resultsGrouped$PRODUCT_P5,
resultsGrouped$PRODUCT_P6,
resultsGrouped$PRODUCT_P7,
resultsGrouped$PRODUCT_P8,
resultsGrouped$PRODUCT_P9,
resultsGrouped$PRODUCT_P10,
resultsGrouped$PRODUCT_P11,
resultsGrouped$PRODUCT_P12,
resultsGrouped$PRODUCT_P13,
resultsGrouped$PRODUCT_P14,
resultsGrouped$PRODUCT_P15,
resultsGrouped$PRODUCT_P16,
resultsGrouped$PRODUCT_P17,
resultsGrouped$PRODUCT_P18,
resultsGrouped$PRODUCT_P19,
resultsGrouped$PRODUCT_P20,
resultsGrouped$PRODUCT_P21,
resultsGrouped$PRODUCT_P22,
resultsGrouped$PRODUCT_P23,
resultsGrouped$PRODUCT_P24,
resultsGrouped$PRODUCT_P25,
resultsGrouped$PRODUCT_P26,
resultsGrouped$PRODUCT_P27,
resultsGrouped$PRODUCT_P28,
resultsGrouped$PRODUCT_P29,
resultsGrouped$PRODUCT_P30)

resultsGrouped$PRODUCT_P1<- NULL
resultsGrouped$PRODUCT_P2<- NULL
resultsGrouped$PRODUCT_P3<- NULL
resultsGrouped$PRODUCT_P4<- NULL
resultsGrouped$PRODUCT_P5<- NULL
resultsGrouped$PRODUCT_P6<- NULL
resultsGrouped$PRODUCT_P7<- NULL
resultsGrouped$PRODUCT_P8<- NULL
resultsGrouped$PRODUCT_P9<- NULL
resultsGrouped$PRODUCT_P10<- NULL
resultsGrouped$PRODUCT_P11<- NULL
resultsGrouped$PRODUCT_P12<- NULL
resultsGrouped$PRODUCT_P13<- NULL
resultsGrouped$PRODUCT_P14<- NULL
resultsGrouped$PRODUCT_P15<- NULL
resultsGrouped$PRODUCT_P16<- NULL
resultsGrouped$PRODUCT_P17<- NULL
resultsGrouped$PRODUCT_P18<- NULL
resultsGrouped$PRODUCT_P19<- NULL
resultsGrouped$PRODUCT_P20<- NULL
resultsGrouped$PRODUCT_P21<- NULL
resultsGrouped$PRODUCT_P22<- NULL
resultsGrouped$PRODUCT_P23<- NULL
resultsGrouped$PRODUCT_P24<- NULL
resultsGrouped$PRODUCT_P25<- NULL
resultsGrouped$PRODUCT_P26<- NULL
resultsGrouped$PRODUCT_P27<- NULL
resultsGrouped$PRODUCT_P28<- NULL
resultsGrouped$PRODUCT_P29<- NULL
resultsGrouped$PRODUCT_P30<- NULL

resultsBinarized <- 
  resultsGrouped %>% 
  group_by(CUSTOMER_ID) %>% 
  summarise(PRODUCT = substr(paste(rev(as.integer(intToBits(sum(strtoi(PRODUCTS, base = 2))))), collapse=""),3,32))

#results binary with frequency
resultsBinarizedWithFrequency <-
  resultsBinarized %>% group_by(PRODUCT) %>% tally() %>% arrange(desc(n))  
```

### Totais por produto
```{r totals-summary}
results %>% group_by(PRODUCT) %>% summarise(TOTAL = n()) %>% arrange(TOTAL) %>% data.table()
```

### Combinations

#### Summary

```{r graph}
resultsGraph <- results %>% mutate(QTD = 1)
resultsGraph %<>% tidyr::spread(PRODUCT, QTD)
resultsGraph[is.na(resultsGraph)] <- 0
resultsGraph %<>% janitor::clean_names()

upset(
  resultsGraph,
  nsets = 30,
  mb.ratio = c(0.5, 0.5),
  order.by = c("freq", "freq"),
  decreasing = c(TRUE,TRUE)
)
```

```{r}
resultsAsTransactions <- read.transactions("results.csv", format = "single", sep = ";", cols = c(1,2))
summary(resultsAsTransactions)
```

#### Distinct combinations of products
```{r}
resultsBinarized %>% group_by("PRODUCT") %>% summarize(cnt = n())
```

#### With more than 0.5% of total users

```{r}
rules2 <- arules::apriori(resultsAsTransactions, parameter = list(supp = 0.005, conf = 0, target = "frequent itemsets"))
plot(rules2)
inspect(rules2)
```

### Clustering - Products approach

```{r clusters-by-product}
source("fill_bucket.R")
```

Following criterias were used:

* No repetition of products in buckets;
* Buckets have same amount of products;
* Buckets in decreasing order of total users.

#### Bucket1

```{r}
print(bucket1)
```

#### Bucket2

```{r}
print(bucket2)
```

#### Bucket3

```{r}
print(bucket3)
```

#### Bucket4

```{r}
print(bucket4)
```

#### Bucket5

```{r}
print(bucket5)
```


### Clustering - Users approach

```{r clusters-by-users}
source("fill_bucket_by_users.R")
```

Following criterias were used:

* No repetition of users in buckets;
* Buckets dont necessarily have same amount of products;
* Buckets in decreasing order of total users.

#### Bucket1

```{r}
print(paste0("Total users: ", buckets$bucket1$n))
print("Products:")
bucket1_configs %>% purrr::reduce(c) %>% unique      
```

#### Bucket2

```{r}
print(paste0("Total users: ", buckets$bucket2$n))
print("Products:")
bucket2_configs %>% purrr::reduce(c) %>% unique      
```

#### Bucket3

```{r}
print(paste0("Total users: ", buckets$bucket3$n))
print("Products:")
bucket3_configs %>% purrr::reduce(c) %>% unique      

```

#### Bucket4

```{r}
print(paste0("Total users: ", buckets$bucket4$n))
print("Products:")
bucket4_configs %>% purrr::reduce(c) %>% unique      

```

#### Bucket5

```{r}
print(paste0("Total users: ", buckets$bucket5$n))
print("Products:")
bucket5_configs %>% purrr::reduce(c) %>% unique      

```

#### Bucket6

```{r}
print(paste0("Total users: ", buckets$bucket6$n))
print("Products:")
bucket6_configs %>% purrr::reduce(c) %>% unique      

```
